---
title: "How to run automated assessment"
author: "Emma Jones"
date: "February 11, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(sf)
library(readxl)
library(FSA)
library(lubridate)
library(magrittr)

# Bring in Assessment functions from app
source('global.R')
```

This document walks users through runing the automated assessement for their region. Prior to this point, the user needs to have completed the necessary prerequisites. This dataset is a companion to the rivers and streams assessment application and is **NOT** final. The results cited in this table are identical to the app calculations and are meant for assessor review, QA, editing prior to finalizing.

# Prerequisites
The user will have to have all conventionals data, water column metals, and sediment metals organized by Roger for the window. Additionally, the EDAS data needs to be exported and available for use. Last cycle's finalized regional assessment layer (shapefile with AUs) are the spatial component needed. Lastly, the assessor must have the stations 2.0 table for the upcoming cycle completely filled out in order to run the assessment. 

```{r datasources}
# Regional AU layer from last cycle
regionalAUs <- st_read('GIS/AU_BRRO_2016_WGS84.shp')

# Roger's conventionals data pull
conventionals <- suppressWarnings(read_csv('data/CONVENTIONALS_20171010.csv'))
conventionals$FDT_DATE_TIME2 <- as.POSIXct(conventionals$FDT_DATE_TIME, format="%m/%d/%Y %H:%M")

# Roger's metals data pull
WCmetals <- read_excel('data/WATER_METALS_20170712.xlsx')
Smetals <- read_excel('data/SEDIMENT_20170712.xlsx')

# Bring in latest EDAS VSCI and (combined) VCPMI queries
VSCI <- read_excel('data/Family Metrics VSCI Calculation.xlsx')%>%
  filter(RepNum == 1 & Target_Count == 110 &
           CollDate >= assessmentPeriod[1] )
VCPMI <- read_excel('data/Family Metrics - CPMI Combined.xlsx')%>%
  filter(RepNum == 1 & Target_Count == 110 &
           CollDate >= assessmentPeriod[1] )

stationTable <- read_csv('data/RegionalResults_AU_WQS.csv') %>%
  # fix periods in column names from excel
  as_tibble() %>%
  dplyr::rename(`Point Unique Identifier` ="Point.Unique.Identifier", `Buffer Distance` = "Buffer.Distance")
```


# Data manipulation

Now that we have all the data we need to run the assessment, we need to reorganize it to run smoothly through the app assessment functions. 

```{r data manipulation}

conventionals_HUC<- left_join(conventionals, dplyr::select(stationTable, FDT_STA_ID, SEC, CLASS, 
                                                           SPSTDS, ID305B_1, ID305B_2, ID305B_3,
                                                           STATION_TYPE_1, STATION_TYPE_2, STATION_TYPE_3), by='FDT_STA_ID') %>%
  left_join(WQSvalues, by = 'CLASS')



AUData <- filter(conventionals_HUC, ID305B_1 %in%'VAW-I09R_JKS06A00' | 
                   ID305B_2 %in% 'VAW-I04R_JKS01A00' | 
                   ID305B_2 %in% 'VAW-I04R_JKS01A00')%>% 
  left_join(WQSvalues, by = 'CLASS')


   output$stationSelection_ <- renderUI({ req(conventionals_HUC(), input$AUSelection)
    z <- filter(conventionals_HUC(), ID305B_1 %in% input$AUSelection | 
                   ID305B_2 %in% input$AUSelection | 
                   ID305B_2 %in% input$AUSelection) %>%
      distinct(FDT_STA_ID)
    selectInput('stationSelection', 'Station Selection', choices = unique(z$FDT_STA_ID))  })
  
  AUData <- eventReactive( input$AUSelection, {
    filter(conventionals_HUC(), ID305B_1 %in% input$AUSelection | 
             ID305B_2 %in% input$AUSelection | 
             ID305B_2 %in% input$AUSelection) %>% 
      left_join(WQSvalues, by = 'CLASS') }) 
  
  stationData <- eventReactive( input$stationSelection, {
    filter(AUData(), FDT_STA_ID %in% input$stationSelection) })
  
```


# Automated assessment


```{r}
stationTableResults <- monStationTemplate

for(i in 1:nrow(stationTable)){
  print(paste('Assessing station', i, 'of', nrow(stationTable), sep=' '))

  # pull one station data
  stationData <- filter(conventionals_HUC, FDT_STA_ID %in% stationTable$FDT_STA_ID[i]) 
  
  # separate objects bc some data smashing issues  
  StationTablePrelimStuff <- StationTableStartingData(stationData)
  
  # Fix forced NA's from character to real NA
  z <- StationTablePrelimStuff %>%
      mutate_all(as.character)
  z[z =="NA"] <- NA
  # manipulate ID305B_1 to get DCR11 watershed ID
  watID <-  substr(strsplit(as.character(z$ID305B_1), '-')[[1]][2] , 1, 3)
  z$WATERSHED_ID <- watID 
  # full station table
  results <- cbind(z, #StationTableStartingData(stationData),
                   tempExceedances(stationData),
                   DOExceedances_Min(stationData), 
                               pHExceedances(stationData),
                               bacteriaExceedances_OLD(bacteria_Assessment_OLD(stationData, 'E.COLI', 126, 235),'E.COLI') %>% 
                                 dplyr::rename('ECOLI_VIO' = 'E.COLI_VIO', 'ECOLI_SAMP'='E.COLI_SAMP', 'ECOLI_STAT'='E.COLI_STAT'),
                               bacteriaExceedances_OLD(bacteria_Assessment_OLD(stationData, 'ENTEROCOCCI', 35, 104),'ENTEROCOCCI') %>% 
                                 dplyr::rename('ENTER_VIO' = 'ENTEROCOCCI_VIO', 'ENTER_SAMP'='ENTEROCOCCI_SAMP', 'ENTER_STAT'='ENTEROCOCCI_STAT'),
                               metalsExceedances(filter(WCmetals, FDT_STA_ID %in% stationData$FDT_STA_ID) %>% 
                                                   dplyr::select(`ANTIMONY HUMAN HEALTH PWS`:`ZINC ALL OTHER SURFACE WATERS`), 'WAT_MET'),
                               acuteNH3exceedance(stationData) %>% # ammonia function being a pain so forcing it in
                                 dplyr::select(AcuteAmmonia_VIO, AcuteAmmonia_STAT) %>% 
                                 dplyr::rename('WAT_TOX_VIO' ='AcuteAmmonia_VIO','WAT_TOX_STAT' = 'AcuteAmmonia_STAT'),
                               metalsExceedances(filter(Smetals, FDT_STA_ID %in% stationData$FDT_STA_ID) %>% 
                                                   dplyr::select(`ACENAPHTHENE`:ZINC), 'SED_MET') %>%
                                 dplyr::select(-ends_with('exceedanceRate')),
                               data.frame(SED_TOX_VIO='Not Analyzed by App', SED_TOX_STAT='Not Analyzed by App'),# Placeholder for sediment toxics
                               data.frame(FISH_MET_VIO='Not Analyzed by App', FISH_MET_STAT='Not Analyzed by App'), # Placeholder for fish metals
                               data.frame(FISH_TOX_VIO='Not Analyzed by App', FISH_TOX_STAT='Not Analyzed by App'),# Placeholder for fish toxics
                               benthicAssessment(stationData,conventionals_sf,VSCI,VCPMI),
                               countTP(stationData),
                               countchla(stationData),
                               data.frame(COMMENTS= as.character('Not Analyzed by App'))) %>%
    dplyr::select(-ends_with('exceedanceRate'))
  
  stationTableResults[i,] <- results
  ## Fix forced NA's from character to real NA
  #z <- StationTablePrelimStuff %>%
  #    mutate_all(as.character)
  #z[z =="NA"] <- NA
  ## manipulate ID305B_1 to get DCR11 watershed ID
  #watID <-  substr(strsplit(as.character(z$ID305B_1), '-')[[1]][2] , 1, 3)
  #z$WATERSHED_ID <- watID 
  # Ammonia gets special section bc problematic
  #AMM <- acuteNH3exceedance(stationData) %>% # ammonia function being a pain so forcing it in
  #  dplyr::select(AcuteAmmonia_VIO, AcuteAmmonia_STAT) %>% 
  #  dplyr::rename('WAT_TOX_VIO' ='AcuteAmmonia_VIO','WAT_TOX_STAT' = 'AcuteAmmonia_STAT') # Placeholder for water toxics
  #more <- cbind(metalsExceedances(filter(Smetals, FDT_STA_ID %in% stationData$FDT_STA_ID) %>% 
  #                                  dplyr::select(`ACENAPHTHENE`:ZINC), 'SED_MET') %>%
  #                dplyr::select(-ends_with('exceedanceRate')),
  #              data.frame(SED_TOX_VIO='Not Analyzed by App', SED_TOX_STAT='Not Analyzed by App'),# Placeholder for sediment toxics
  #              data.frame(FISH_MET_VIO='Not Analyzed by App', FISH_MET_STAT='Not Analyzed by App'), # Placeholder for fish metals
  #              data.frame(FISH_TOX_VIO='Not Analyzed by App', FISH_TOX_STAT='Not Analyzed by App'),# Placeholder for fish toxics
  #              benthicAssessment(stationData,conventionals_sf,VSCI,VCPMI),
  #              countTP(stationData),
  #              countchla(stationData),
  #              data.frame(COMMENTS= 'Not Analyzed by App')) %>% 
  #  dplyr::select(-ends_with('exceedanceRate'))
  #z2 <- cbind(z, StationTableResults1, AMM, more)
  

}

siteData$StationTablePrelimStuff <- StationTableStartingData(stationData()))

siteData$StationTableResults1 <- cbind(tempExceedances(stationData()), 
                                                 DOExceedances_Min(stationData()), pHExceedances(stationData()),
                                                 bacteriaExceedances_OLD(bacteria_Assessment_OLD(stationData(), 'E.COLI', 126, 235),'E.COLI') %>% 
                                                   dplyr::rename('ECOLI_VIO' = 'E.COLI_VIO', 'ECOLI_SAMP'='E.COLI_SAMP', 'ECOLI_STAT'='E.COLI_STAT'),
                                                 bacteriaExceedances_OLD(bacteria_Assessment_OLD(stationData(), 'ENTEROCOCCI', 35, 104),'ENTEROCOCCI') %>% 
                                                   dplyr::rename('ENTER_VIO' = 'ENTEROCOCCI_VIO', 'ENTER_SAMP'='ENTEROCOCCI_SAMP', 'ENTER_STAT'='ENTEROCOCCI_STAT'),
                                                 
                                                 metalsExceedances(filter(WCmetals, FDT_STA_ID %in% stationData()$FDT_STA_ID) %>% 
                                                                     dplyr::select(`ANTIMONY HUMAN HEALTH PWS`:`ZINC ALL OTHER SURFACE WATERS`), 'WAT_MET'))%>%
            dplyr::select(-ends_with('exceedanceRate'))

z <- siteData$StationTablePrelimStuff%>%
      mutate_all(as.character)
    z[z =="NA"] <- NA
    watID <-  substr(strsplit(as.character(z$ID305B_1), '-')[[1]][2] , 1, 3)
    z$WATERSHED_ID <- watID 
    AMM <- acuteNH3exceedance(stationData()) %>% # ammonia function being a pain so forcing it in
      dplyr::select(AcuteAmmonia_VIO, AcuteAmmonia_STAT) %>% 
      dplyr::rename('WAT_TOX_VIO' ='AcuteAmmonia_VIO','WAT_TOX_STAT' = 'AcuteAmmonia_STAT')#data.frame(WAT_TOX_VIO='Not Analyzed by App', WAT_TOX_STAT='Not Analyzed by App'),# Placeholder for water toxics
    more <- cbind(metalsExceedances(filter(Smetals, FDT_STA_ID %in% stationData()$FDT_STA_ID) %>% 
                                      dplyr::select(`ACENAPHTHENE`:ZINC), 'SED_MET') %>%
                    dplyr::select(-ends_with('exceedanceRate')),
                  data.frame(SED_TOX_VIO='Not Analyzed by App', SED_TOX_STAT='Not Analyzed by App'),# Placeholder for sediment toxics
                  data.frame(FISH_MET_VIO='Not Analyzed by App', FISH_MET_STAT='Not Analyzed by App'), # Placeholder for fish metals
                  data.frame(FISH_TOX_VIO='Not Analyzed by App', FISH_TOX_STAT='Not Analyzed by App'),# Placeholder for fish toxics
                  benthicAssessment(stationData(),conventionals_sf,VSCI,VCPMI),
                  countTP(stationData()),
                  countchla(stationData()),
                  data.frame(COMMENTS= 'Not Analyzed by App')) %>% dplyr::select(-ends_with('exceedanceRate'))
    z2 <- cbind(z, siteData$StationTableResults1, AMM, more)
    
```

